\chapter{Introduction}\label{sec:intro}

\section{Topic covered}\label{sec:}


\section{Keywords}\label{sec:}
Biometrics, pattern recognition, authentication, healthmonitoring, internet of
things, smart devices, \glspl{ws}, eletronics, accelerometer.

\section{Problem description}\label{sec:}
In todays world many electronic devices has flooded the market and been taken
into use by the public.  The latest swarm of devices are wearable electronic
devices, eg. healthmonitors, \gls{imd}, \glspl{swatch} and wearable devices.
All of which are capable of logging data for different purposes.

This project focuses on area of \glspl{ws} which provide healthmonitoring
by logging \gls{bio} data about its user and to which end this type of data is
applicable to other areas like authentication / identification, realtime
detection of medical emergencies ie. fall detection, cardiac arrest, and the
case of health monitoring over a prolonged time for detection of deterioration
or emerging issues, eg. parkinsons desease or cardio vascular issues.

At this point in time, the leading brands of \glspl{ws} don't provide
access to their wearable devices. Meaning the data has to be synced to their
online \gls{cloud} service for storage, before it can be retrieved for analysis.
Obviously this poses a real issue for real time events like authentication and
identification procedures, or medical emergencies. In addition the idea of
storing personal data about health in the \gls{cloud} and through an untrusted third
party poses issues for both healthcare legislation and authentication
procedures.

Because of these problems, this project will try to ascertain how applicable the
use of wearable sensor are for identification and authentication, and healthcare
monitoring on a realtime basis and prolonged time.  The sensor data which are
interesting includes data from "FitBit" devices which includes heart rate, 
accelleration, gyroscope and \Gls{gnss}, and smartphone devices, which include 
video, audio, gyroscope, accelleration and fingerprint data.

\section{Justification motivation and benefits}\label{sec:}


\section{Research questions}\label{sec:}

\begin{itemize}
\item Is \gls{ots} wearable devices applicable for real time health
	monitoring and authentication / identification?

\item Is \gls{ots} wearable devices applicable for prolonged health
	monitoring

\item What data is required to perform either of the tasks in question?

\item 

\item 

\item What type of data is gathered by current \gls{ots} wearable devices,
	and in what form is it available?

\begin{itemize}
	\item Must the project develop its own sensor to get the data required?
	\item How is the required one measure heart rate using electronic devices?
	\item 
\end{itemize}

\item 

\begin{itemize}
\item 
\end{itemize}

\item 

\end{itemize}


\section{Planned contributions}\label{sec:}


